Supplementary material S2: Disturbance simulations

### 2018-01-26 S1.Rmd
Draft 0.1.9001 Init from the article draft branch

# Appendix 2: Leaf lifespan model

@@

## Material and methods

@@

## Results

@@

>>>>

---
title: "Supplementary material S1: Leaf lifespan model"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    number_sections: false
    toc: false
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

@@

# Material and methods

@@

# Results

@@

# References

### 2018-01-26 S2.Rmd
Draft 0.1.9001 Init from the article draft branch

# Appendix 5: Disturbance simulations

@@

## Ecosystem functions

@@

## Biodiversity effect

>>>>

---
title: "Supplementary material S2: Disturbance simulations"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    number_sections: false
    toc: false
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

```{r config, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls()); invisible(gc())
library(knitr)
library(ggplot2)
opts_chunk$set( echo = F, message = F, warning = F, 
                fig.height = 8, fig.width = 8,
                cache = T, cache.lazy = F)
```

@@

# Ecosystem functions

@@

# Biodiversity effect
